A novel method for detecting coalescing binaries in near realtime with Advanced LIGO and beyond \editorial{Submit to PRD or CQG?}

### 2011-02-19 results.tex
added description of triggers
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@654 ccdd05d5-56c1-461a-bf98-85f6876523b4

\subsection{Trigger reduction procedure}

{\color{red} Describe triggering, clustering, injection finding, injection re-weighting, and \textsc{roc} plotting here.}

>>>>

\subsection{Triggering and data reduction}

For each template with parameters $\theta_i$, a trigger is recorded any time the absolute value of the \textsc{snr}, $|\rho(\theta_i)|$, is greater than a threshold $\rho^* = 5.5$, and is also a maximum over the 10~ms before and after. \editorial{This is a proposed trigger criterion that is much simpler than what we currently use.} A trigger is therefore an ordered triple $(t, i, \rho)$, recording the time, template number, and complex \textsc{snr} of an excursion in the outputs of the matched filter bank.

Offline, triggers for all templates collectively are clustered by time, such that within a sliding window of 4 seconds, all triggers except the one with the highest $\rho$ is kept.

For the injection-free passes, all clustered triggers are regarded as false alarms.  We accumulate the \textsc{snr}s of all of the false alarms into the set $\{|\rho|\}_\mathrm{false\,alarm}$.

For each injection, we check whether there was any clustered trigger that was within 2 seconds of the injection's time.  If there was, then the injection is considered to be recovered at the \textsc{snr} of that trigger.  Otherwise, the injection was not recovered because the \textsc{snr} threshold $\rho^*$ was not met, so we consider the injection to be recovered only at an \textsc{snr} of $\infty$.  From all found injections, we accumulate the injected distance and the recovered \textsc{snr} into the set $\{(d, |\rho|)\}_\mathrm{found}$.
